\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{setspace}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Aditya Bichave} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{(+91) 7798497481 \\ Bangalore, India} 
\address{\href{mailto:aditya.bichave@gmail.com}{aditya.bichave@gmail.com} \href{https://www.linkedin.com/in/aditya-bichave/}{https://www.linkedin.com/in/aditya-bichave/}}%

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{BRIEF SUMMARY}
\linespread{1.0}
{ I am a skilled Software Engineer with\textbf{ 4+ years experience} in building large-scale, scalable, \textbf{distributed systems}. Proficient in \textbf{Python, Java, Golang, Big-Data, Django, Spring Boot, SQL, Docker, AWS}. Effective communicator, able to work independently or collaboratively with stakeholders. Seeking opportunities to leverage experience for positive organizational impact }


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor  of Computer Science}, Pune University \hfill { 2017 - 2021}\\
Course: Computer Science \hfill CGPA: 9.1/10\\ 
Relevant Courses: Algorithms, Data Structures, Object-Oriented software development process, Java, Python, Operating  Systems, Database Management Systems, Distributed Systems, Network Security, Big data

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{0.65\textwidth} }
Platforms & Docker, Google Cloud Platform, Amazon Web Services \\
Data & Amazon RDS, NoSQL Databases, PostgreSQL, MySQL, Redis, MongoDB, Aerospike, Amazon DynamoDB \\
Computer Languages & Python, SQL, Java 8, Java \\
Frameworks & Spring Data, Hibernate, Spring Core, JUnit, Spring Security, PyTorch, Mockito, Django, Spring Boot, JUnit 5, Spring MVC \\
Web/Application Servers & Web Services \\
Solutions & Postman, Amazon S3, AWS CloudFormation, Amazon Elastic File System, Amazon EC2 \\
Standards & API \& Integration Standards, REST API \\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer 2}, EPAM \hfill Jul 2024 - Present\\
\textbf{Senior Software Engineer}, Uber \hfill Oct 2024 - Jul 2025\\
 \hfill \textit{Bangalore, Karnataka}
 \begin{itemize}
    \itemsep -6pt
    \item Executed end-to-end migration of critical microservices from legacy TChannel transport to the scalable YARPC framework.
    \item Refactored service interfaces in Java 8+, enabling YARPC HTTP/gRPC transports with Thrift/Protobuf encoding while preserving API contracts.
    \item Integrated YARPC services with Spring Boot to separate transport and business logic through modular layers.
    \item Authored migration patterns and templates to accelerate adoption across Java microservices.
 \end{itemize}

\textbf{Software Engineer 2}, Sandvine \hfill Oct 2021 - June 2024\\
 \hfill \textit{Bangalore, Karnataka}
 \begin{itemize}
    \itemsep -6pt 
     \item \textbf{IBCM}:  Developed an innovative in-house distributed systems Intent-Based Congestion Management (IBCM), optimizing performance and enhancing \textbf{Quality of Experience} (QoE) which helped \textbf{reduce network congestion} by\textbf{ 15\%}.
    \item \textbf{Perf}: Optimized existing codebase for \textbf{60\% performance} scalability, leveraging strong analytical skills.
    \item \textbf{OCE}: Designed high-level and low-level architecture for \textbf{Real-time} Link Bandwidth Estimation, \textbf{increasing revenue} by \textbf{\$250K quarterly per license}. Led this project and received a \textbf{performance champion award}. 
    \item \textbf{Database}: Took ownership of database optimization, Designing and implementing Database Async Writer feature for \textbf{30\% performance improvemen}t in IBCM and OCE. used \textbf{SQL} (vertica) for storage and \textbf{Redis} for Caching for faster data access. Used \textbf{Big Data} concepts for more optimized Data Storage, Data ingestion and Data Processing. 
    \item \textbf{Load Balancing}: Developed a distributed system for load balancing to \textbf{scale and increase} the product's processing capability by\textbf{ 25\%}. Designed and Implemented support for \textbf{Cloud Deployment}  with multi-cluster multi-node \textbf{High availability} setup
    \item \textbf{Infra}: Led codebase \textbf{migration} for major system, achieving \textbf{4X performance} improvement. Spearheaded this initiative by \textbf{Mentoring and guiding} achieving efficient memory usage and scaled performance
    \item \textbf{Features}: Led development of key features including Real-time Operational capacity  estimation, Async Database Writer Service,  High Availability, Geo Redundancy, Multi-Cluster Support, and Licensing by Subscriber Count, among others by Leveraging Rest API, Aerospike, and Microservice concepts. 
    \item \textbf{Customers}: Supported customer-facing and cross-functional teams in deploying, designing  and implementing POC  to enhance the product experience.

 \end{itemize}
 
\textbf{Software Development Engineer Test}, Pubmatic \hfill Jun 2021 - Oct 2021\\
 \hfill \textit{Pune, Maharashtra}
 \begin{itemize}
    \itemsep -6pt 
     \item Automated Ad revenue monetization testing pipeline, Enhanced debugging skills through troubleshooting
    \item Adapted quickly to new technologies and methodologies in the fast-paced AdTech sector
 \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\itemsep -6pt 
\item \textbf{Grid Compression Using autoencoders.} {A solutions to store the mechanical projects of 5-6 TB by compressing}
\item \textbf{Space Detection In Floor Plan DL.} {A solutions to help the government body to rectify and find issues.}
\item \textbf{Eyantra Homecoming Project Hackathon.} {DL computer vision project which led to qualification for the competition organized by IIT-Bombay.}
\end{rSection} 



\begin{rSection}{ACHIEVEMENTS}

\itemsep -6pt 
\item \textbf{Published Patent} {App for providing corona vaccine in efficient way}
\item \textbf{Won Hackathon} {Won annual hackathon in Sandvine for automating Setting up the MAE environment based on configuration.}
\item \textbf{Eyantra Finalist, IIT bombay.} {Awarded for qualifying for finals for deep learning competition organized by IIT Bombay.}
\end{rSection} 

\end{document}
